### 2019-02-12 2-Chapters/1-Chapter/chapter1.tex
Okay for tikz figure showing outline of the thesis
Ok for tex root

%!TEX root = ../thesis.tex

@@

% ----------------------------------------------------------------------------
\section{List of publications}
\label{sec:1:contributions}

>>>>

%!TEX root = ../PhD_thesis__Lilian_Besson

@@

% ----------------------------------------------------------------------------
\section{Organization of the thesis}
\label{sec:1:organization}

Here we discuss quickly the organization of the thesis.

\begin{figure}[h!]
    \centering
    \resizebox{0.85\textwidth}{!}{
    \begin{tikzpicture}[>=latex',line join=bevel,scale=3]
        %
        \node[align=center] (introduction) at (0,2.5) [rectangle,draw] {Chapter~\ref{chapter:1}\\Introduction};
        \node[align=center] (chapter2) at (0,2) [rectangle,draw] {Chapter~\ref{chapter:2}\\Multi-Armed Bandit models};
        \node[align=center] (chapter3) at (4,2) [rectangle,draw] {Chapter~\ref{chapter:3}\\SMPyBandits: simulation\\library for MAB};
        \node[align=center] (chapter4) at (-2,1) [rectangle,draw] {Chapter~\ref{chapter:4}\\Two MAB models for IoT networks};
        \node[align=center] (chapter5) at (0,1) [rectangle,draw] {Chapter~\ref{chapter:5}\\Multi-players MAB};
        \node[align=center] (chapter6) at (2,1) [rectangle,draw] {Chapter~\ref{chapter:6}\\Non-stationary MAB models};
        \node[align=center] (conclusion) at (0,0) [rectangle,draw] {Chapter~\ref{chapter:conclusion}\\General conclusion};
        %
        \draw [color=black,thick,->] (introduction) to (chapter2);
        \draw [color=black,thick,<->] (chapter2) to (chapter3);
        \draw [color=black,thick,->] (chapter2) to (chapter4);
        \draw [color=black,thick,->] (chapter2) to (chapter5);
        \draw [color=black,thick,->] (chapter2) to (chapter6);
        \draw [color=black,thick,->] (chapter4) to (conclusion);
        \draw [color=black,thick,->] (chapter5) to (conclusion);
        \draw [color=black,thick,->] (chapter6) to (conclusion);
        %
    \end{tikzpicture}
    }
    \caption{Organization of the thesis.}
    \label{fig:1:organization}
\end{figure}

% ----------------------------------------------------------------------------
\section{List of publications}
\label{sec:1:listPublications}

### 2019-02-12 2-Chapters/2-Chapter/chapter2.tex
Ok for tex root

\subsection{Applications for Opportunistic Spectrum Access}

@@

% ----------------------------------------------------------------------------
\section{A short review of famous MAB algorithms}
\label{sec:2:famousMABalgorithms}

@@

\subsection{Regret lower bounds}

- [Lai and Robbins] lower-bound in $\Omega(\log(T))$
- Worst case lower in $\Omega(\sqrt{T})$

@@

\subsection{Numerical computation of Kullback-Leibler divergences and klUCB indexes}

@@

>>>>

\subsection{Application for Opportunistic Spectrum Access}

@@

% ----------------------------------------------------------------------------
\section{Review of MAB algorithms}
\label{sec:2:famousMABalgorithms}

@@

\subsection{Regret lower bounds: do not detail too much, don't explain the tools behind the results}

- [Lai and Robbins] lower-bound in $\Omega(\log(T))$
- Worst case lower-bound in $\Omega(\sqrt{T})$
- Adversarial lower-bound in $\Omega(\sqrt{T})$ (also useful for piece-wise stationary models)

@@

\subsection{Eficient numerical computation of Kullback-Leibler divergences and \klUCB{} indexes}

@@

My work for this part is also published on https://github.com/Naereen/Kullback-Leibler-divergences-and-kl-UCB-indexes
(in Python) and https://github.com/Naereen/KullbackLeibler.jl (in Julia).

### 2019-02-12 2-Chapters/3-Chapter/chapter3.tex
Started to copy/paste my latest paper
Ok for tex root

% ----------------------------------------------------------------------------
\section{An example of another model: rested or restless Markov models}
\label{sec:3:markovModels}

@@

@@

Include verbatim the file
\verb{example_of_main_singleplayer.py}

@@

Include verbatim the file
\verb{example_of_configuration_singleplayer.py}

>>>>

% ----------------------------------------------------------------------------
\section{An example of another model: rested or restless Markov models - FIXME maybe not included?}
\label{sec:3:markovModels}

@@

\begin{minted}[mathescape,
    linenos,
    numbersep=5pt,
    gobble=2,
    frame=lines,
    framesep=2mm]{csharp}
string title = "This is a Unicode π in the sky"
/*
Defined as $\pi=\lim_{n\to\infty}\frac{P_n}{d}$ where $P$ is the perimeter
of an $n$-sided regular polygon circumscribing a
circle of diameter $d$.
*/
const double pi = 3.1415926535
\end{minted}

@@

Include verbatim the file
\texttt{example\_of\_main\_singleplayer.py}

% \lstinputlisting[language=Python]{2-Chapters/3-Chapter/src/example_of_main_singleplayer.py}

@@

Include verbatim the file
\texttt{example\_of\_configuration\_singleplayer.py}

% \lstinputlisting[language=Python]{2-Chapters/3-Chapter/src/example_of_configuration_singleplayer.py}
